### 2020-03-04 doc/icfp20/harmony.tex

In Haskell this would be easy---there is an \texttt{Eq} type class and a
method for automatically generating equalities. In the Agda Standard
Library~\citep{agda-stdlib} list membership is a relation with
constructive evidence of membership, and requires far more effort we
would like given that we currently don't need to do
proofs. Alternatives include defining decidable equality for triads
(which requires writing out 49 cases) or mapping to natural numbers
and using already implemented decidable or boolean equality for
those. For now we simply write the inverse function manually,
excluding the rare cases.

@@

We next restrict to progressions ending in a half cadence (V) to match
Piston's example (\texttt{filter halfCadence}). This results in 25
candidate progressions. For each pitch and triad pair we construct a
\texttt{harmonizingChord} in root position with the root doubled. The
function \texttt{voiceChord} spaces the notes nicely. All of this work
is done in the function \texttt{voicedHarmonizations}.

>>>>

In Haskell this would be easy---there is an \texttt{Eq} type class and a
method for automatically generating equalities. In the Agda Standard
Library~\citep{agda-stdlib} list membership is a relation with
constructive evidence of membership, and requires far more effort than we
would like given that we currently don't need to do
proofs. Alternatives include defining decidable equality for triads
(which requires writing out 49 cases) or mapping to natural numbers
and using already implemented decidable or boolean equality for
those. For now we simply write the inverse function manually,
excluding the rare cases.

@@

We next restrict to progressions ending in a half cadence (V) to match
Piston's example. This results in 25
candidate progressions. For each pitch and triad pair we construct a
\texttt{harmonizingChord} in root position with the root doubled. The
function \texttt{voiceChord} spaces the notes nicely. All of this work
is done in the function \texttt{voicedHarmonizations}.
